Stability of Dynamical System Ensembles

### 2014-09-10 journal.tex
finish 3x3 simulation

@@

\section{$2 \times 2$ systems}
We call a matrix stable when the real part of all its eigenvalues is negative.  For a $2 \times 2$ matrix, this amounts to the conditions $T < 0$ and $D >
0$ where $T$ and $D$ denote the trace and the determinant.

@@

\begin{table}[h]
\begin{tabular}{ c || c | c }
\hline
matrix & \specialcell{probability of stability\\to perturbation} & probability of stability\\
\hline
  $\begin{pmatrix}
a & b \\
d & c
\end{pmatrix}$ & 0.62 & 0.25 \\
  $\begin{pmatrix}
a & b \\
d & 0
\end{pmatrix}$, $\begin{pmatrix}
0 & b \\
d & c
\end{pmatrix}$ & 0.5 & 0.25 \\
  $\begin{pmatrix}
a & 0 \\
d & c
\end{pmatrix}$, $\begin{pmatrix}
a & b \\
0 & c
\end{pmatrix}$ & 0.67 & 0.25 \\
$\begin{pmatrix}
a & 0 \\
0 & c
\end{pmatrix}$ & 0.5 & 0.25 \\
\end{tabular}
\caption{Probability of matrix stability under resampling and \emph{a priori} stability. All matrices not listed have probability $0$ of stability.}\label{tab:structstabmat}
\end{table}

The probability of \emph{a priori} stability and of stability to perturbations for all $2 \times 2$-matrices are given in Table \ref{tab:structstabmat}.

@@

>>>>

% user added
\usepackage{longtable}

@@

\section{Two component systems}
We call a matrix stable when the real part of all its eigenvalues is negative.  For a $2 \times 2$ matrix, this amounts to the conditions $T < 0$ and $D >
0$ where $T$ and $D$ denote the trace and the determinant.

@@

\begin{table}[h]
\begin{tabular}{ c || c | c | c }
\hline
matrix & connectivity & \specialcell{probability of stability\\to perturbation} & probability of stability\\
\hline
  $\begin{pmatrix}
a & b \\
d & c
\end{pmatrix}$ & 4 & 0.62 & 0.25 \\
  $\begin{pmatrix}
a & b \\
d & 0
\end{pmatrix}$, $\begin{pmatrix}
0 & b \\
d & c
\end{pmatrix}$ & 3 & 0.5 & 0.25 \\
  $\begin{pmatrix}
a & 0 \\
d & c
\end{pmatrix}$, $\begin{pmatrix}
a & b \\
0 & c
\end{pmatrix}$ & 3 & 0.67 & 0.25 \\
$\begin{pmatrix}
a & 0 \\
0 & c
\end{pmatrix}$ & 2 & 0.5 & 0.25 \\
\end{tabular}
\caption{{\bf Probability of stability under resampling and \emph{a priori} stability for two component systems derived analytically}. All matrices not listed have $0$ probability of stability.}\label{tab:structstabmat}
\end{table}

The probability of \emph{a priori} stability and of stability to perturbations for all two component systems is given in Table \ref{tab:structstabmat}.

@@

\section{Three component systems}

The probability of \emph{a priori} stability and of stability to perturbations for all three component systems is given in Table \ref{tab:structstabmat3}.

% \begin{table}[h]
\begin{longtable}{ c || c | c | c }
\hline
matrix & connectivity & \specialcell{probability of stability\\to perturbation} & probability of stability\\
\hline
$\begin{pmatrix}
1 & 0 & 0\\
0 & 1 & 0\\
0 & 0 & 1\\
\end{pmatrix}$ & 4 & 0.496 & 0.125\\
$\begin{pmatrix}
0 & 0 & 1\\
0 & 0 & 1\\
1 & 1 & 0\\
\end{pmatrix}$ & 5 & 0.117 & 0.07\\
$\begin{pmatrix}
0 & 0 & 1\\
0 & 1 & 0\\
1 & 0 & 1\\
\end{pmatrix}$ & 5 & 0.49 & 0.123\\
$\begin{pmatrix}
1 & 0 & 0\\
0 & 1 & 1\\
0 & 0 & 1\\
\end{pmatrix}$ & 5 & 0.62 & 0.128\\
$\begin{pmatrix}
0 & 0 & 1\\
0 & 0 & 1\\
1 & 1 & 1\\
\end{pmatrix}$ & 6 & 0.32 & 0.089\\
$\begin{pmatrix}
0 & 0 & 1\\
0 & 1 & 1\\
1 & 0 & 1\\
\end{pmatrix}$ & 6 & 0.599 & 0.123\\
$\begin{pmatrix}
0 & 0 & 1\\
0 & 1 & 1\\
1 & 1 & 0\\
\end{pmatrix}$ & 6 & 0.499 & 0.127\\
$\begin{pmatrix}
0 & 1 & 1\\
0 & 0 & 1\\
1 & 0 & 1\\
\end{pmatrix}$ & 6 & 0.398 & 0.064\\
$\begin{pmatrix}
0 & 1 & 0\\
0 & 1 & 1\\
1 & 0 & 1\\
\end{pmatrix}$ & 6 & 0.431 & 0.08\\
$\begin{pmatrix}
0 & 1 & 1\\
0 & 1 & 0\\
1 & 0 & 1\\
\end{pmatrix}$ & 6 & 0.597 & 0.126\\
$\begin{pmatrix}
0 & 1 & 1\\
0 & 1 & 1\\
1 & 0 & 0\\
\end{pmatrix}$ & 6 & 0.41 & 0.061\\
$\begin{pmatrix}
1 & 0 & 1\\
0 & 1 & 1\\
0 & 0 & 1\\
\end{pmatrix}$ & 6 & 0.7 & 0.122\\
$\begin{pmatrix}
1 & 0 & 0\\
0 & 1 & 1\\
0 & 1 & 1\\
\end{pmatrix}$ & 6 & 0.595 & 0.123\\
$\begin{pmatrix}
1 & 0 & 1\\
0 & 1 & 0\\
0 & 1 & 1\\
\end{pmatrix}$ & 6 & 0.701 & 0.125\\
$\begin{pmatrix}
0 & 0 & 1\\
0 & 1 & 1\\
1 & 1 & 1\\
\end{pmatrix}$ & 7 & 0.574 & 0.117\\
$\begin{pmatrix}
0 & 1 & 1\\
0 & 0 & 1\\
1 & 1 & 1\\
\end{pmatrix}$ & 7 & 0.486 & 0.075\\
$\begin{pmatrix}
0 & 1 & 1\\
0 & 1 & 1\\
1 & 0 & 1\\
\end{pmatrix}$ & 7 & 0.539 & 0.092\\
$\begin{pmatrix}
0 & 1 & 0\\
0 & 1 & 1\\
1 & 1 & 1\\
\end{pmatrix}$ & 7 & 0.497 & 0.088\\
$\begin{pmatrix}
0 & 1 & 1\\
0 & 1 & 0\\
1 & 1 & 1\\
\end{pmatrix}$ & 7 & 0.664 & 0.126\\
$\begin{pmatrix}
0 & 1 & 1\\
0 & 1 & 1\\
1 & 1 & 0\\
\end{pmatrix}$ & 7 & 0.482 & 0.086\\
$\begin{pmatrix}
0 & 1 & 1\\
1 & 1 & 0\\
1 & 0 & 1\\
\end{pmatrix}$ & 7 & 0.589 & 0.126\\
$\begin{pmatrix}
1 & 0 & 1\\
0 & 1 & 1\\
0 & 1 & 1\\
\end{pmatrix}$ & 7 & 0.66 & 0.127\\
$\begin{pmatrix}
1 & 1 & 1\\
0 & 1 & 1\\
0 & 0 & 1\\
\end{pmatrix}$ & 7 & 0.749 & 0.121\\
$\begin{pmatrix}
1 & 1 & 0\\
0 & 1 & 1\\
1 & 0 & 1\\
\end{pmatrix}$ & 7 & 0.61 & 0.097\\
$\begin{pmatrix}
0 & 1 & 1\\
0 & 1 & 1\\
1 & 1 & 1\\
\end{pmatrix}$ & 8 & 0.571 & 0.102\\
$\begin{pmatrix}
0 & 1 & 1\\
1 & 0 & 1\\
1 & 1 & 1\\
\end{pmatrix}$ & 8 & 0.472 & 0.077\\
$\begin{pmatrix}
0 & 1 & 1\\
1 & 1 & 1\\
1 & 0 & 1\\
\end{pmatrix}$ & 8 & 0.59 & 0.11\\
$\begin{pmatrix}
1 & 1 & 1\\
0 & 1 & 1\\
0 & 1 & 1\\
\end{pmatrix}$ & 8 & 0.709 & 0.125\\
$\begin{pmatrix}
1 & 0 & 1\\
0 & 1 & 1\\
1 & 1 & 1\\
\end{pmatrix}$ & 8 & 0.642 & 0.122\\
$\begin{pmatrix}
1 & 1 & 1\\
0 & 1 & 1\\
1 & 0 & 1\\
\end{pmatrix}$ & 8 & 0.63 & 0.108\\
$\begin{pmatrix}
0 & 1 & 1\\
1 & 1 & 1\\
1 & 1 & 1\\
\end{pmatrix}$ & 9 & 0.57 & 0.092\\
$\begin{pmatrix}
1 & 1 & 1\\
0 & 1 & 1\\
1 & 1 & 1\\
\end{pmatrix}$ & 9 & 0.649 & 0.111\\
$\begin{pmatrix}
1 & 1 & 1\\
1 & 1 & 1\\
1 & 1 & 1\\
\end{pmatrix}$ & 10 & 0.645 & 0.103\\
\caption{{\bf Probability of stability under resampling and \emph{a priori} stability for three component systems estimated via Monte Carlo sampling.} All matrices not listed have $0$ probability of stability.}\label{tab:structstabmat3}
\end{longtable}
%
% \end{table}
